The \dealii Library, Version 9.7

### 2025-08-02 9.7/paper.tex
Remove the simplex / mixed-mesh section.
Minor edits.

\dealii version 9.7.0 was released July 22, 2025.
\todo{Update}
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.7. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
terms of the \emph{GNU Lesser General Public License} (LGPL). The \dealii
project is in the process of relicensing the library under the terms of
the \emph{Apache License 2.0 with LLVM Exception}. Downloads are
available at \url{https://www.dealii.org/} and
\url{https://github.com/dealii/dealii}.

The major changes of this release are:
%
\begin{itemize}
\item
  \todo[inline]{Update list from the subsections below}
\end{itemize}
%

@@

\subsection{Support for simplex and mixed meshes}

\todo[inline]{I moved the `improved anisotropic split' change listed here to the
  `other changes' section.}

\todo[inline]{Are there other noteworthy changes}

>>>>

\dealii version 9.7.0 was released July 22, 2025.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.7. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
terms of the \emph{GNU Lesser General Public License} (LGPL). The \dealii
project is in the process of relicensing the library under the terms of
the \emph{Apache License 2.0 with LLVM Exception}. Downloads are
available at \url{https://www.dealii.org/} and
\url{https://github.com/dealii/dealii}.

The major changes of this release are:
%
\begin{itemize}
\item
  \todo[inline]{Update list from the subsections of Section 2
    below. Like in the previous release papers, we here basically give
  a 1-3 sentence summary of the subsections 2.x, with a link to that section.}
\end{itemize}
%

@@

%% The major simplex additions are the changes to
%% convert_hypercube_to_simplex_mesh() and MappingP1: those are discussed
%% elsewhere so we don't need a dedicated section for the general topic
